Advantages of mixed unitary operators for quantum information processing

### 2018-12-29 decorrelation/mixed_unitaries.tex
some small formatting changes to equation 22

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}

@@

\begin{equation}\label{eq:minimization_regularization}
\begin{split}
\underset{n\in[N]}{\textbf{minimize}}\{\\
    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega||+ \eta\sum\omega_j||H_j||_2 + t\\
&\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
&\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\\
\}
\end{split}
\end{equation}

@@

% ==============================================================================
% Section: Acknowledgements
% ==============================================================================
\section{Acknowledgements}
\label{sec:acknowledgements}
Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S. Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.

\begin{figure*}[h]
  \centering
  \includegraphics[width=\textwidth]{SQRTY.png}
  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$. The results are quantitatively similar to those for $RX(\frac{\pi}{2})$. In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin. However, varying over $\delta$ we see that the 1MUP outperforms the 0MUP by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
  \label{fig:YMUP}
\end{figure*}

@@

\bibliography{decorrelation.bib}
\end{document}

>>>>

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}

@@

\newcommand{\bunderbrace}[2]{%
  \begin{array}[t]{@{}c@{}}
  #1\\
  \parbox{\widthof{#1}}{$\scriptscriptstyle#2$}
  \end{array}
}

\begin{equation}\label{eq:minimization_regularization}
\begin{split}
&\underset{n\in[N]}{\textbf{minimize}}\{\\
&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||D_{\ell}^T\omega||+ \eta\sum\omega_j||H_j||_2 + t\\
&\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
&\ \ \phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\\
\}
\end{split}
\end{equation}

@@

% ==============================================================================
% Section: Acknowledgements
% ==============================================================================
\section{Acknowledgements}
\label{sec:acknowledgements}
Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S. Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.
\bibliography{decorrelation.bib}

\newpage
\onecolumngrid
% ==============================================================================
% Section: Appendix
% ==============================================================================
\section{Appendix}
\label{sec:appendix}
\begin{figure*}[h]
  \centering
  \includegraphics[width=\textwidth]{SQRTY.png}
  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$. The results are qualitatively similar to those for $RX(\frac{\pi}{2})$. In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin. However, varying over $\delta$ we see that the 1MUP outperforms the 0MUP by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
  \label{fig:YMUP}
\end{figure*}

@@

\end{document}
